---
title: "SLR_superconductivity"
author: "Sowmya, Disha, Anushka, Pranjali, Ashmita"
date: "19/12/2021"
output: pdf_document
---


```{r include=FALSE}
# Don't delete this chunk if you are using the mosaic package
# This loads the mosaic and dplyr packages
require(mosaic)
```

```{r include=FALSE}
# knitr settings to control how R chunks work.
require(knitr)
opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small"    # slightly smaller font for code
)
# This loads the mosaic data sets.  (Could be deleted if you are not using them.)
require(mosaicData)
```

# Summary:

## Aim: 
## Plotting Linear Regression for best correlated variable with "critical temperature" in superconductivity data.

## Steps:
## Finding most correlated variables
## Exploratory Analysis for these variables to understand more about them
## Finding trend of correlated variables with target variable "critical_temp" to find which variable is best for SLR
## Checking assumptions for SLR and performing SLR
## Checking if the model is a good fit

```{r cars}
sconduct <- read.csv('C:/Users/disha/OneDrive/Desktop/501/final project/superconduct/train.csv')
ncol(sconduct)

sconduct_x <- subset(sconduct, select = -critical_temp)
sconduct_y <- sconduct['critical_temp']
names_col = names(sconduct)
names_col
```

## Finding most correlated variables

```{r}
df2 = cor(sconduct)
df2 = df2[,82] # only select correlation with critical temp

df2 = sort(df2, decreasing = TRUE)
df2

```
## Picking the 5 variables that vary lineary (hit and trial gave these best variables varying linearly, even though correlation might be less)

## Exploratory Analysis for these variables to understand more about them

Index used :

            0 : entropy_atomic_mass                     
            1 : wtd_std_atomic_radius
            2 : wtd_entropy_FusionHeat
            3 : wtd_entropy_Valence
            4 : wtd_range_ThermalConductivity
                             
\textbf{All variables continuous, quantitative except number of elements}
```{r}
bwplot(~entropy_atomic_mass, data=sconduct)

bwplot(~wtd_std_atomic_radius, data=sconduct)

bwplot(~wtd_entropy_FusionHeat, data=sconduct)

bwplot(~wtd_entropy_Valence, data=sconduct)

bwplot(~wtd_range_ThermalConductivity, data=sconduct)

```


```{r}
xyplot(critical_temp ~ entropy_atomic_mass, data=sconduct)

xyplot(critical_temp ~ wtd_std_atomic_radius, data=sconduct)

xyplot(critical_temp ~ wtd_entropy_FusionHeat, data=sconduct)

xyplot(critical_temp ~ wtd_entropy_Valence, data=sconduct)

xyplot(critical_temp ~ wtd_range_ThermalConductivity, data=sconduct)

```

## Fitting the linear model on these variables and Checking assumptions for these 5 variables

## Fit 
```{r}
# entropy_atomic_mass
xyplot(critical_temp ~ entropy_atomic_mass, sconduct, type=c("p", "r"))
lm0 <- lm(critical_temp ~ entropy_atomic_mass, sconduct)
summary(lm0)

```

```{r}
# wtd_std_atomic_radius
xyplot(critical_temp ~ wtd_std_atomic_radius, sconduct, type=c("p", "r"))
lm1 <- lm(critical_temp ~ wtd_std_atomic_radius, sconduct)
summary(lm1)
```


```{r}
# wtd_entropy_FusionHeat
xyplot(critical_temp ~ wtd_entropy_FusionHeat, sconduct, type=c("p", "r"))
lm2 <- lm(critical_temp ~ wtd_entropy_FusionHeat, sconduct)
summary(lm2)
```


```{r}
# wtd_entropy_Valence
xyplot(critical_temp ~ wtd_entropy_Valence, sconduct, type=c("p", "r"))
lm3 <- lm(critical_temp ~ wtd_entropy_Valence, sconduct)
summary(lm3)
```


```{r}
# wtd_entropy_atomic_mass
xyplot(critical_temp ~ wtd_range_ThermalConductivity, sconduct, type=c("p", "r"))
lm4 <- lm(critical_temp ~ wtd_range_ThermalConductivity, sconduct)
summary(lm4)
```

# Check assumptions

# 1. Linearity : Verified (appears linear)
# 2. Independence : Assume true
# 3. Residuals Normal : 
```{r}
par(mfrow=c(5, 2))
histogram(~ residuals(lm0), nint=10)
xqqmath(~resid(lm0))

histogram(~ residuals(lm1), nint=10)
xqqmath(~resid(lm1))

histogram(~ residuals(lm2), nint=10)
xqqmath(~resid(lm2))

histogram(~ residuals(lm3), nint=10)
xqqmath(~resid(lm3))

histogram(~ residuals(lm4), nint=10)
xqqmath(~resid(lm4))

```
Histogram : 
Can assume Normal: 4
Not sure due to skewness: 0, 1, 2, 3

QQPlot : 
Perfect Normal: None
Moderate Normal : All

## 4. Equal Variance Assumption:
```{r}
xyplot(residuals(lm0) ~ fitted(lm0), type=c("p", "r"))

xyplot(residuals(lm1) ~ fitted(lm1), type=c("p", "r"))

xyplot(residuals(lm2) ~ fitted(lm2), type=c("p", "r"))

xyplot(residuals(lm3) ~ fitted(lm3), type=c("p", "r"))

xyplot(residuals(lm4) ~ fitted(lm4), type=c("p", "r"))

```
Since the residuals do not look fairly evenly scattered about the horizontal line of 0 in any of the plots, are assumption is not getting justified for this dataset (tried many variables).
Also the R-squared is not very great (~0.30-0.34 for all graphs).

We should not fit regression on this dataset.

F-test
Look at the tables and write results. Mention formulae.

t-test
Look at the table and write results. Mention formulae.

